---
title: 'R Package: scRabble'
author: Stacy Kam
date: '2018-06-13'
slug: r-package-scrabble
categories: [R]
tags: [R Package]
---
 
```{r setup, include=FALSE}
library(scRabble)
```

# scRabble Package

This package was made by Aaron Balleisen and myself, and the basic idea behind is a the game Scrabble. This package contains functions that would be helpful while playing scrabble but are also useful for other hundred of applications. This package contains the following functions: 

1. get_words()
2. points()
3. is_word()
4. num_words()

# get_words() 

The attributes for this function are: a string of characters, and optional length of output words, and optional wildcard (allows system to add any letter that might make a new word with existing string). This function will return a list of words that can be made with the constraints set. 

For instance, you might decide to get all existing words with the letters: a, b, and c
```{r}
get_words("abce")
```

You might also want just with words with at most 3 letters: 
```{r}
get_words("abc", 3)
```

And to make it a little more exciting, you might even want to add a wildcard: 
```{r}
get_words("abc", 3, TRUE)
```

# num_word() 

If you don't feel like looking at all the words that can be created, but rather just know how many words exist with all the different combinatins of the word, you can just call this function with the same parameters as get_words() and it will return the amount. 

```{r}
num_words("abc", 3, TRUE)
```

# points() 

The attributes for this function are: a string representing a word, a list containing location followed by multiplier (in pairs) representing the double/triple letter points, and an int representing how many times we should multiply the word by double or triple points. The only mandatory attribute is the word by itself. This will return the amount of points generated by the word in a real game of scrabble. 

```{r message=FALSE, warning=FALSE}
points("botch", c(1,2,1,2,1), dw = 2)
```

# is_word() 

The only attribute for this function is simple a string representing a word, and this function will return a statement communicating if the word exists or not. This function was made to dispute all those fights about determining if a word exists or not. 

```{r message=FALSE, warning=FALSE}
is_word("hello")
is_word("xcd")
```
