---
title: 'Hackathon Project: Trump Cloud Additions'
author: 'Stacy Kam'
date: '2018-07-03'
slug: hackathon-project-trump-cloud-additions
categories: [hackathon]
tags: [hackathon, R, R package, shinyapp, wordcloud]
---

# Feature Additions

I added a UI input text feature so that the user could specify tweets that contain the word `Trump` and whatever word the user wants. For example if you want to know the exact feeling of people tweeting about `Trump` and `children` now you can!

# The Code

### Text Input on the UI on Shiny App:

``` {r, echo=TRUE}
textInput("filter", "Filter Word:", value = "")
```

### Applying the input on the server:

``` {r, echo=TRUE}
fetch <- reactive({
    d <- tweets(input$date, input$filter)
    word_bag <- clean_data(d)
    final_scoring <- sentiments_score(word_bag)
    return(final_scoring)
  })
```

### Adding the new attribute to the function:

```{r, echo=TRUE}
tw = twitteR::searchTwitter(paste0("Trump ", "+ ", filter_word), n = 2500,
                              since = as.character(inputdate - 1), until = as.character(inputdate),
                              lang = 'en', retryOnRateLimit = 1e3)
```